Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-15 paper/paper.tex
complete feature and metric sections

\documentclass{sig-alternate-05-2015}

@@

@@

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage{hyperref}

@@

\subsection{Discussion}
It seems that Arisholm's contribution to the community with Cost Effectiveness back in  2010 has provided a better metric to evaluate fault prediciton models going forward.  Seeing as the point of fault prediction should be to build tools that can be used in the real world for real projects injecting the realism that CE brings to the table seems to be totally appropriate in going forward.  Even though that is viewed as the case by some in the community confusion matrix based approaches and the related ROC curve concept are seemingly going nowhere.  These approaches will continue to be important in evaluating models until something better comes along.

Our recommendation in this area would be to work with a hybrid approach of using both confusion matrix approaches and the ROC curve as well as CE based metrics.  The suggestion of Hall as listed above to simply report confusion matrices seems like a great recommendation when possible going forward.  At that point researchers could simply report cost effectiveness data along with confusion matrices and leave any further analysis to those that are interested.  If reporting confusion matrices were not to become popular, settling on one confusion matrix based approach such as the F-Measure would be preferable to the random mixture of reporting approaches viewed throughout our papers.

@@

\subsection{Text Classification}
The paper on Personalized Defect Prediction by Jiang et al uses a methodology based on change classification \cite{Jiang}.  To understand the metrics involved it was necessary to go back to a paper by Kim et al and get an idea of exactly what was done for feature extraction \cite{Kim}.  The basic methodology uses process metrics such as changed LOC between commits, and when commits take place, but also uses traditional techniques like LOC, and complexity analysis.

The more interesting and complex aspect of both of these papers is text classification.  They both use a tool called BOW (Bag Of Words) to pull features out of log messages (called metadata in Jiang et all) and source code.  The metadata aspect of this approach is also used in the Arisholm paper under the name Deltas where it is stated as simply the change between releases and also calls it Code Churn \cite{Arisholm}.  Code churn in later papers is simply subsumed into process metrics, where later survey papers like Radjenovic simply categorize them together \cite{Radjenovic}.

The source code inspection can be incredibly low level as in the Kim paper where they "This (text classification) means that every variable, method name, function name, keyword, comment word, and operator, that is everything  in the source code separated by whitespace or a semicolon is used as a feature"\cite{Kim}.  The Jiang paper pulled out features like incorrect calls of individual language level functions like malloc and calloc on a per developer basis and then used those to predict faults for individual developers.  It is an intriguing approach and one that was successful based on Jiang's results, It is an approach that has been cited, but not repeated.  Partially that may be because the paper is fairly recent having been published in 2013, but it may also owe something to the fact that this is a seemingly intensive effort that few would use in industry.

\subsection{Benchmark Data Sets}

In one of our most recent papers (the Nam paper 2013 \cite{Nam}) we found researchers using benchmark data sets that had sets of metrics that could be chosen from in order to build models.  The two sets discussed in the paper are ReLink and AEEEM \cite{Wu} \cite{DAmbros}.

D'Ambros' AEEEM seemingly took everything he could find that he could rationalize and some new ideas and then just threw all of it into a metric set.  \href{http://bug.inf.usi.ch/}{AEEEM} includes: change metrics, CK metrics, Object Oriented metrics, number of previous defects, complexity of code change, churn of CK and OO metrics, entropy of CK and OO metrics.  ReLink unfortunately was not as helpful in listing out what is available in terms of metrics.  Based on the Nam paper it contains 26 complexity metrics \cite{Nam}.

\subsection{Discussion}
As can be seen by the length and complexity of this section, the metrics area is still a very open area in fault defect prediction.  The simple fact that there are major differences in terms of what metric set is being used across different projects creates some difficulty when comparing them.  Also since many of these projects also use a hybrid approach, it makes it even less likely that another project will use exactly the same set of metrics.

There is simply no consensus on what a good metric set really is, and that makes research going forward a difficult proposition.  Our recommendation would be for the community to continue to codify what they believe to be the best metric sets and then to build benchmark data sets like AEEEM and ReLink that can be used across projects so that the approaches of researchers can be appropriately compared.
